---
title: "In-Class1"
author: "Abhishek Singh"
published: "`May 11 2023`"
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
---

Loading Tidyverse
```{r}

pacman::p_load(tidyverse)
```

Importing data
```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

## Working with theme

Changing the colors of plot panel background of theme_minimal() to light blue and the color of grid lines to white.

:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, aes(x=RACE)) +
  geom_bar() +
  coord_flip() +
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "lightblue", colour = "lightblue", 
                                    size = 0.5, linetype = "solid"),
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
    panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, aes(x=RACE)) +
  geom_bar() +
  coord_flip() +
  theme_minimal() +
  theme(
    panel.background = element_rect(fill = "lightblue", colour = "lightblue", 
                                    size = 0.5, linetype = "solid"),
    panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
    panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

```
:::
## Designing Data-drive Graphics for Analysis I


:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x=reorder(RACE,RACE,
                     function(x)-length(x)))) +
  geom_bar() +
  ylim(0,220) +
  geom_text(stat="count", 
      aes(label=paste0(..count.., ", ", 
      round(..count../sum(..count..)*100, 1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils") +
  theme(axis.title.y=element_text(angle = 0))
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x=reorder(RACE,RACE,
                     function(x)-length(x)))) +
  geom_bar() +
  ylim(0,220) +
  geom_text(stat="count", 
      aes(label=paste0(..count.., ", ", 
      round(..count../sum(..count..)*100, 1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils") +
  theme(axis.title.y=element_text(angle = 0))

```
:::

This code chunk uses fct_infreq() of forcats package.

:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
exam_data %>%
  mutate(RACE = fct_infreq(RACE)) %>%
  ggplot(aes(x = RACE)) + 
  geom_bar()+
  ylim(0,220) +
  geom_text(stat="count", 
      aes(label=paste0(after_stat(count), ", ", 
      round(after_stat(count)/sum(after_stat(count))*100,
            1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils") +
  theme(axis.title.y=element_text(angle = 0))
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
exam_data %>%
  mutate(RACE = fct_infreq(RACE)) %>%
  ggplot(aes(x = RACE)) + 
  geom_bar()+
  ylim(0,220) +
  geom_text(stat="count", 
      aes(label=paste0(after_stat(count), ", ", 
      round(after_stat(count)/sum(after_stat(count))*100,
            1), "%")),
      vjust=-1) +
  xlab("Race") +
  ylab("No. of\nPupils") +
  theme(axis.title.y=element_text(angle = 0))

```
:::

## Designing Data-drive Graphics for Analysis II

- Adding mean and median lines on the histogram plot.
- Change fill color and line color

:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x= MATHS)) +
  geom_histogram(bins=20, 
                 color="black", 
                 fill="light blue") +
  geom_vline(aes(xintercept=mean(MATHS, na.rm=T)),
             color="red", 
             linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(MATHS, na.rm=T)),
             color="grey30",
             linetype="dashed", 
             size=1)
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x= MATHS)) +
  geom_histogram(bins=20, 
                 color="black", 
                 fill="light blue") +
  geom_vline(aes(xintercept=mean(MATHS, na.rm=T)),
             color="red", 
             linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(MATHS, na.rm=T)),
             color="grey30",
             linetype="dashed", 
             size=1)

```
:::

## Designing Data-drive Graphics for Analysis III

:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
d <- exam_data   
d_bg <- d[, -3]  
ggplot(d, aes(x = ENGLISH, fill = GENDER)) +
  geom_histogram(data = d_bg, fill = "grey", alpha = .5) +
  geom_histogram(colour = "black") +
  facet_wrap(~ GENDER) +
  guides(fill = 'none') +  
  theme_bw()
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(d, aes(x = ENGLISH, fill = GENDER)) +
  geom_histogram(data = d_bg, fill = "grey", alpha = .5) +
  geom_histogram(colour = "black") +
  facet_wrap(~ GENDER) +
  guides(fill = 'none') +  
  theme_bw()

```
:::

## Designing Data-drive Graphics for Analysis IV

:::panel-tabset

## Plot
```{r}
#| echo: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x=MATHS, y=ENGLISH)) +
  geom_point() +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  geom_hline(yintercept=50,
             linetype="dashed",
             color="grey60",
             size=1) + 
  geom_vline(xintercept=50, 
             linetype="dashed",
             color="grey60",
             size=1)
```

## Code

```{r}
#| eval: false
#| fig-width: 4
#| fig-height: 4
ggplot(data=exam_data, 
       aes(x=MATHS, y=ENGLISH)) +
  geom_point() +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  geom_hline(yintercept=50,
             linetype="dashed",
             color="grey60",
             size=1) + 
  geom_vline(xintercept=50, 
             linetype="dashed",
             color="grey60",
             size=1)

```
:::


## Tableau 

*Links to Tableau Visualisations:*


[Superstore Orders](https://public.tableau.com/app/profile/abhishek.singh2379/viz/SuperstoreDashboard_16815425205270/Dashboard1)
